---
title: "pair.generator package intro"
author: "Ken Bredemeyer"
date: "16 March 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Generating Pairs for Pairwise Comparisons

The `pair.generator` package pairs performances or media items for use in a pairwise comparison project.

All functions begin with `pairs_`.  That makes it easy to search for all functions in the package.  Function documentation can be accessed using `?pairs_make`, etc.

### Installation

Install using
`devtools::install_github(“KenBredemeyer/pair.generator”)`


### Usage
Load the package using
```{r load}
library(pair.generator)
```

The main function for generating pairs is `pairs_make()`.  This function takes as it's input a `data.frame` containing the variables `media` (character), `core` (integer), `score` numeric.  `pairs.make()` will not work with factors.

Read in data using
`p_data <- pairs_import.csv('*scores file.csv*')`.  This function calls `read.csv(..., stringsAsFactors = FALSE)` and then does some checks on the data.

Alternatively, use
`read.csv('*scores file.csv', stringsAsFactors = FALSE)`
or
`readr::read_csv('*scores file.csv')`
just make sure that `media` is a character vector, not factors.

pair.generator has two built in data sets, `data_standard` and `data_cnc`.  Bring a data set into the global environment for inspection using
```{r}
data(data_standard)
```

This vignette will use the built in data sets to demonstrate generating pairs.

Pair performances (media labels) to make a new scale using
```{r pairs_make}
gp <- pairs_make(data_standard,
	               type = "standard_pairs",
	               min_c = 8, max_c = 15,
	               chaining_constant = 4)
head(gp)
```

`min_c` is the desired minimum number of inclusions (or comparisons involved in) per performance.
`max_c` is the desired maximum number of inclusions (or comparisons involved in) per performance.
`chaining_constant` is the number of consecutive pairs containing a common performance.

In the output, `combination` is the row number of the set of all possible combinations ordered alphabetically.

Test the number of inclusions per performance in the set of generated pairs (`gp`) using
```{r inclusions_plot}
pairs_plot_inclusions(gp)
```

To export pairs as a .csv file, use
`pairs_export(gp, "*filename*.csv")`
